Conference Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-03-19 paper.tex
Add Authors Info

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

>>>>

\author{\IEEEauthorblockN{Khaled Amgad\IEEEauthorrefmark{1},
Mahmoud Mohamad\IEEEauthorrefmark{2}, Muhanad Atef\IEEEauthorrefmark{3} and
Nader AbdAlGhani\IEEEauthorrefmark{4}}
\IEEEauthorblockA{Computer Engineering Dept.,
Faculty of Engineering, Cairo University\\
Cairo, Egypt\\
\IEEEauthorrefmark{1}khaled.mohamed98@eng-st.cu.edu.eg,
\IEEEauthorrefmark{2}mmmacmp@gmail.com,
\IEEEauthorrefmark{3}muhanad.atef23@gmail.com,
\IEEEauthorrefmark{4}nader\_abdelghani@hotmail.com}}
